RNA-seq from 4 cell populations

### 2021-11-01 deconvolution/fans4/molec_profiling.Rmd
add per cell type analysis

# cd /hpc/users/hoffmg01/work/cmc_analysis/src
cd /hpc/users/hoffmg01/work/CMC/covarr-de/deconvolution/fans4
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
R

@@

```{r}
CODE <- Folder(name = "results", parentId = "syn26433312")
CODE <- synStore(CODE)

@@

Correlation between cell types
```{r corr.celltype}
C = get_pairwise_sharing( resMash )

>>>>

# cd /hpc/users/hoffmg01/work/cmc_analysis/src
cd /hpc/users/hoffmg01/work/CMC/covarr-de/deconvolution/fans4
# rm -rf molec_profiling_cache/
ml git pandoc python
git pull
R

@@

```{r storeData}
CODE <- Folder(name = "results", parentId = "syn26433312")
CODE <- synStore(CODE)

@@

Correlation between cell types
```{r corr.celltype}
library(corrplot)
C = get_pairwise_sharing( resMash )
